He-Man: A domain-specific language for lightweight concurrency

### 2012-03-06 paper/paper.tex
Changed font size for reality check.
Add arg packet figure.

\title{He-Man: A domain-specific language for lightweight concurrency}
%\subtitle{I said hey, what's goin' on}
\authorinfo{Carlo Angiuli}{Carnegie Mellon University}{cangiuli@cs.cmu.edu}
\authorinfo{Michael Sullivan}{Carnegie Mellon University}{mjsulliv@cs.cmu.edu}

@@

\begin{abstract}
% XXX: better abstract;
% and where should we put the code link?
% we should also move it to some better URL

@@

>>>>

%XXX: new title?
\title{He-Man: A domain-specific language for lightweight concurrency}
%\subtitle{I said hey, what's goin' on}
\authorinfo{Carlo Angiuli}{Carnegie Mellon University}{cangiuli@cs.cmu.edu}
\authorinfo{Michael Sullivan}{Carnegie Mellon University}{mjsulliv@cs.cmu.edu}

@@

\begin{abstract}
% XXX: better abstract;
% and where should we put the code link?

@@

\begin{figure}[ht]
\centering
\begin{code}
class ArgPacket a b | a -> b, b -> a where
  toIExprList :: a -> [IExpr]
  makeVars :: [String] -> a
class ArgDecls a b | a -> b, b -> a where
  toVDecl :: a -> [VDecl]

instance ArgPacket (Expr a) [a] where
  toIExprList (E x) = [x]
  makeVars [x] = E (Var x)
instance ArgPacket (Expr a, Expr b) (a, b) where
  toIExprList (E x1, E x2) = [x1, x2]
  makeVars [x1, x2] = (E (Var x1), E (Var x2))
-- ...

instance ArgDecls (TVDecl a) [a] where
  toVDecl (x1, t1) = [(x1, toIType t1)]
instance ArgDecls (TVDecl a, TVDecl b) (a, b) where
  toVDecl ((x1, t1), (x2, t2)) =
    [(x1, toIType t1), (x2, toIType t2)]
-- ...

declare_thread :: (ArgPacket a c, ArgDecls b c) =>
                  b -> (a -> Prog ()) ->
                  ThreadCode c
declare_thread = ...
spawn :: ArgPacket a b => ThreadCode b -> a ->
                          Prog ()
spawn = ...
call :: ArgPacket a b => Prim -> Type c -> a ->
                         Prog (Expr c)
call = ...

\end{code}
\caption{He-Man argument packets} % XXX
\label{fig:arg-packets}
\end{figure}
